% ---------------------------------------------------------
% PACKAGE CONFIGURATIONS
% ---------------------------------------------------------
\lstset{
    basicstyle=\ttfamily\scriptsize,
    breaklines=true,
    keywordstyle=\color{blue},
    stringstyle=\color{darkgray},
    commentstyle=\color{gray},
    frame=single,
    showstringspaces=false
}

% ---------------------------------------------------------
% SYSTEM ARCHITECTURE
% ---------------------------------------------------------
\begin{frame}{System Architecture}
    \begin{block}{Platform Components}
        An end-to-end MLOps ecosystem designed for dynamic feature extraction, hyperparameter shifting, and localized storage.
    \end{block}
    \begin{itemize}\scriptsize
        \item \textbf{Data Ingestion Pipeline:} Handles modular ingestion via structured CSV files securely bounded by project root configurations.
        \item \textbf{Feature Engineering Pipeline:} \texttt{DynamicFeatureEngineer} transforms raw inputs into interaction terms and indicators.
        \item \textbf{Adaptive ML Optimization:} Runs sequential multi-stage Optuna tuning loops with real-time MLflow Tracking metrics.
        \item \textbf{Model Registry:} Tracks parameters and logs serialized cloudpickle models to a dedicated SQLite storage layer.
        \item \textbf{API Inference Service:} Implements microservices using FastAPI to deliver endpoints for execution and runtime statistics.
    \end{itemize}
\end{frame}

% ---------------------------------------------------------
% CHURN PREDICTION WORKFLOW
% ---------------------------------------------------------
\begin{frame}{Churn Prediction Workflow}
    \begin{alertblock}{Data Lifecycle Execution}
        From raw transaction parameters to calculated strategic customer retention campaigns.
    \end{alertblock}
    \begin{enumerate}\scriptsize
        \item \textbf{Customer Input Data:} Raw structured vectors pass through validation checks upon reaching API micro-routers.
        \item \textbf{Feature Transformation:} Preprocessors construct feature names out, scaling variables using target encodings.
        \item \textbf{Pipeline Type Defense:} An implicit \texttt{XGBNumericCaster} layer forces features into \texttt{float32} shapes to shield the base boosting trees.
        \item \textbf{Model Inference:} High-velocity tree tracking models run predictive passes to assign probability weights.
        \item \textbf{X-Ray Explanations:} Triggers localized tree-path dependent SHAP routines to serialize feature importances back to MLflow.
    \end{enumerate}
\end{frame}

% ---------------------------------------------------------
% MULTI-STAGE TRAINING ENGINE
% ---------------------------------------------------------
\begin{frame}{Adaptive Multi-Stage Optimization Loop}
    \begin{itemize}
        \item Implements sequential search boundary adjustment loops over 4 key phases to scale parameter ranges dynamically:
    \end{itemize}
    \begin{table}\scriptsize
        \centering
        \begin{tabular}{lcl}
            \toprule
            \textbf{Optimization Phase} & \textbf{Trials Run} & \textbf{Search Boundary Strategy} \\
            \midrule
            Base Phase & 200 & Explores baseline hyperparam defaults \\
            Phase 2 Step & 100 & Quantile profiling and range movement \\
            Phase 3 Step & 50 & Concentrates boundaries on optimum zones \\
            Phase 4 Step & 25 & Fine-tunes localized high-perf vectors \\
            \bottomrule
        \end{tabular}
        \caption{Sequential Parameter Convergence Lifecycle}
    \end{table}
    \begin{block}{Model Promotion \& Champion Guardrails}
        The tracking server queries all parent runs inside the SQLite environment. The platform automatically promotes new models only if the calculated test PR-AUC surpasses the highest historical metric.
    \end{block}
\end{frame}

% ---------------------------------------------------------
% CORE INTERFACE ROUTING (FASTAPI)
% ---------------------------------------------------------
\begin{frame}[fragile]{Microservice Interface Endpoints}
    The delivery layer exposes clean REST schemas managed by Uvicorn.
    \begin{lstlisting}[language=Python]
# Ingestion and Retraining 
@app.post("/train")
async def train(file: UploadFile, experiment_name: str):
    # Runs ingestion, engineering, and multi-stage loops

# Real-Time Operational Predictor
@app.post("/predict")
async def predict(file: UploadFile, run_id: str):
    # Transforms arrays and produces XGBoost probabilities

# Analytics and Audit
@app.get("/experiments/best_runs")
def get_best_runs():
    # Returns history tracking logs via BestRunResponse Pydantic schema
    \end{lstlisting}
\end{frame}

% ---------------------------------------------------------
% CONTAINERIZED DEPLOYMENT
% ---------------------------------------------------------
\begin{frame}{Containerized Deployment Architecture}
    \begin{block}{Reproducible Ecosystem Environment}
        The application is packaged inside a lightweight \texttt{python:3.12-slim} container, ensuring quick start-up times and isolation.
    \end{block}
    \begin{itemize}
        \item \textbf{FastAPI Application Container (\texttt{hop\_api}):} Exposes internal operational processing functions via port \texttt{8000}.
        \item \textbf{MLflow Dashboard Service (\texttt{hop\_mlflow}):} Mounts unified workspace directory binds to expose the visualization engine UI on port \texttt{5000}.
        \item \textbf{Persistent Storage Layer:} Mounts localized shared system volumes to maintain tracking information inside \texttt{mlflow.db} and model plots under \texttt{mlartifacts/}.
    \end{itemize}
\end{frame}

% ---------------------------------------------------------
% PRODUCTION MONITORING
% ---------------------------------------------------------
\begin{frame}{Production Monitoring}
    \begin{block}{System Health \& Observability Metrics}
        Proactive telemetry strategy deployed across the serving instance to protect model health over time.
    \end{block}
    \begin{itemize}
        \item \textbf{API Performance Tracking:} Real-time latency profiling, hardware footprint utilization, and HTTP error code tracking.
        \item \textbf{Data Drift Detection:} Baseline distribution auditing to capture shifting inputs before performance degradation occurs.
        \item \textbf{Prediction Profiling:} Continuous logging of predicted churn probabilities to catch out-of-bounds score skews.
        \item \textbf{Automated Alerting Engine:} Model performance degradation thresholds configured to dispatch infrastructure operational notices.
    \end{itemize}
\end{frame}

% ---------------------------------------------------------
% END-TO-END MLOPS PIPELINE
% ---------------------------------------------------------
\begin{frame}{End-to-End MLOps Pipeline}
    \begin{exampleblock}{Continuous Integration \& Training Loop}
        Unified architectural lifecycle mapping feedback dependencies from collection to iteration.
    \end{exampleblock}
    \vspace{0.3cm}
    \begin{center}
        \small
        \colorbox{gray!15}{\textbf{\strut Data}} $\rightarrow$ 
        \colorbox{gray!15}{\textbf{\strut Features}} $\rightarrow$ 
        \colorbox{gray!15}{\textbf{\strut Training}} $\rightarrow$ 
        \colorbox{gray!15}{\textbf{\strut MLflow}} $\rightarrow$ 
        \colorbox{gray!15}{\textbf{\strut Deployment}} $\rightarrow$ 
        \colorbox{gray!15}{\textbf{\strut Monitoring}} $\rightarrow$ 
        \colorbox{gray!15}{\textbf{\strut Retraining}}
    \end{center}
\end{frame}
